\textsc{HubbleCLIP}: Associating Astronomical Observations and Natural Language with Multi-Modal Models

### 2024-01-14 paper/main.tex
Added dot-product plots to paper

The model is evaluated by tracking the loss in Eq.~\ref{eq:softmax_loss} as well as the top-$k\%$ retrieval accuracy on the held out validation set over the course of training. The retrieval accuracy is defined as the fraction of associated captions which fall within the top $k\%$ of captions by cosine similarity of the (normalized) embeddings $(x_i \cdot y_j)$, averaged over the images in the validation set.

@@

@@

>>>>

The model is evaluated by tracking the loss in Eq.~\ref{eq:softmax_loss} as well as the top-$k\%$ retrieval accuracy on the held out validation set over the course of training. The retrieval accuracy is defined as the fraction of associated captions which fall within the top $k\%$ of captions by cosine similarity of the (normalized) embeddings $x_i \cdot y_j$, averaged over the images in the validation set.

@@

\paragraph*{Cosine similarity distribution}

The top row of Figure~\ref{fig:sim_valtrain} shows the distribution of cosine similarities between corresponding image and text embeddings, $x_i$ and $y_i$, for the LLM-summarized abstracts using the fine-tuned CLIP model (red line), with the ordering of text embeddings shuffled (dashed red line), and for the base CLIP model (blue line), shown for the set of validation pairs (top left) and same number of training set pairs (top right). The distribution for the base model is seen to be sharply peaked at a specific value, showing little diversity and being

@@

\begin{figure*}[!h]
\includegraphics[width=0.95\textwidth]{plots/sim_valtrain.pdf}
\centering\includegraphics[width=0.45\textwidth]{plots/sim_summ1.pdf}
\caption{Distribution of cosine similarities between corresponding image and text embeddings, $x_i$ and $y_i$. (Top row) For the LLM-summarized abstracts using the fine-tuned CLIP model (red line), with the ordering of text embeddings shuffled (dashed red line), and for the base CLIP model (blue line), shown for (top left) the set of validation pairs and (top right) same number of training set pairs. (Bottom) For the single-concept summaries, when evaluated using the CLIP model fine-tuned on LLM-summarized abstracts (red) and fine-tuned on the single-concept summaries themselves.}
\label{fig:sim_valtrain}
\end{figure*}
